Epistemic Semantics in Guarded String Models

### 2021-01-14 tex/pdraft.tex
add citations

Epik is closely related to Kleene Algebra with Hypotheses\cite{},
\textsc{Ka+H}, which permits user-specification of futher equations
beyond the axioms of \textsc{Ka}. In practice, these hypotheses are
used to express domain-specific properties of the axioms, such as the
commutativity of certain uninterpreted actions in program
verification, such as $x := 3; y := 5 \equiv y := 5; x := 3$). We can
model both the state formulae and the event formulae as \textsc{KA+H}
hypotheses. Specifically, the state formula $\varphi$ can be thought
of as a hypothesis $\varphi \equiv 1$, and an event formula $\zeta_a$
for event $a$, is simply the hypothesis $a \equiv
\sum_{\varphi,\varphi' \in \llbracket \zeta_a \rrbracket}
\varphi;a;\varphi'$. Notwithstanding some early results about
\textsc{Kat} with hypotheses of the form $cp=c$~\cite{}, using basic
\textsc{KA} implementations would rely on using the exponential
encoding of \textsc{Kat} into \textsc{Ka}~\cite{}.

>>>>

Epik is closely related to Kleene Algebra with Hypotheses
\textsc{Ka+H}~\cite{cohen1994hypotheses}, which permits
user-specification of futher equations beyond the axioms of
\textsc{Ka}. In practice, these hypotheses are used to express
domain-specific properties of the axioms, such as the commutativity of
certain uninterpreted actions in program verification, such as $x :=
3; y := 5 \equiv y := 5; x := 3$). We can model both the state
formulae and the event formulae as \textsc{KA+H} hypotheses.
Specifically, the state formula $\varphi$ can be thought of as a
hypothesis $\varphi \equiv 1$, and an event formula $\zeta_a$ for
event $a$, is simply the hypothesis $a \equiv \sum_{\varphi,\varphi'
  \in \llbracket \zeta_a \rrbracket} \varphi;a;\varphi'$. In general,
the Horn theory of \textsc{KA+H} is undecidable, however many special
cases for \textsc{Ka} and for \textsc{Kat} are
decidable~\cite{doumane2019kleene, hardin2002elimination,
  kozen1997kleenecompleteness}.
